Exploring the Utility of Machine Learning Across Varied Data Formats

### 2024-05-25 homework2/paper/paper.tex
described in the paper the Linear Regression used

@@

% ---- Bibliography ----
\begin{thebibliography}{8}
    \bibitem{}
    \href{https://pandas.pydata.org/docs/reference/api/pandas.DataFrame.html}{Pandas - DataFrame}
    \bibitem{}
    \href{https://en.wikipedia.org/wiki/Correlation}{Wikipedia - Correlation}
    \bibitem{}
    \href{https://thinkingneuron.com/how-to-measure-the-correlation-between-two-categorical-variables-in-python/}{Thinking Neuron - How to Measure the Correlation Between Two Categorical Variables in Python}
    \bibitem{}
    \href{https://www.stratascratch.com/blog/chi-square-test-in-python-a-technical-guide/}{StrataScratch - Chi-Square Test in Python: A Technical Guide}
    \bibitem{}
    \href{https://en.wikipedia.org/wiki/Cram\%C3\%A9r\%27s\_V}{Wikipedia - Cramér's V}
    \bibitem{}

>>>>

In the \textit{linear\_regression} folder at the root of the project directory,
we implemented the Linear Regression algorithm in two different ways:

\begin{itemize}
    \item \textit{Linear Regression with Scikit-Learn:} We used the Scikit-Learn
    library to implement Linear Regression on the preprocessed datasets.
    \item \textit{Linear Regression from Scratch:} We implemented Linear Regression
    as in the 8th laboratory from the Artificial Intelligence course.
\end{itemize}

I choose to implement the RidgeRegression algorithm. Because of the large number of
features in the dataset, the RidgeRegression algorithm is more suitable than the
LinearRegression algorithm. The RidgeRegression algorithm is a regularized version
of Linear Regression that adds a penalty term to the loss function to prevent overfitting.
This penalty term helps to reduce the model's complexity and improve its generalization
performance. The alpha parameter controls the strength of the regularization, with
higher values of alpha leading to stronger regularization. I used the value of alpha
1.75 because it provided the best results in the experiments.

For enconding the categorical attributes except the target attribute, I used the
\textit{OneHotEncoder} class from the \textit{sklearn.preprocessing} module. This
class encodes categorical attributes as one-hot vectors, creating a binary representation
of each category. This encoding is essential for feeding categorical attributes into
machine learning models, as most algorithms require numerical input data. For the
target attribute, I used the \textit{LabelEncoder} class from the \textit{sklearn.preprocessing}
module to encode the target attribute as integer values.

The results of both implementations for each dataset are saved in the \textit{LinearRegression}
folder at the specific dataset's root.

@@

% ---- Bibliography ----
\begin{thebibliography}{8}
    \bibitem{}
    \href{https://curs.upb.ro/2023/course/view.php?id=13749}{Moodle - Artifical Intelligence Course}
    \bibitem{}
    \href{https://en.wikipedia.org/wiki/Linear_regression}{Wikipedia - Linear Regression}
    \bibitem{}
    \href{https://en.wikipedia.org/wiki/Linear_classifier}{Wikipedia - Linear Classifier}
    \bibitem{}
    \href{https://en.wikipedia.org/wiki/Ridge_regression}{Wikipedia - Ridge Regression}
    \bibitem{}
    \href{https://www.semanticscholar.org/reader/2c9022fe0af15568a885e59d475ec8f95726e51b}{Metrics for Multi-Class Classification: An Overview}
    \bibitem{}
    \href{https://pandas.pydata.org/docs/reference/api/pandas.DataFrame.html}{Pandas - DataFrame}
    \bibitem{}
    \href{https://en.wikipedia.org/wiki/Correlation}{Wikipedia - Correlation}
    \bibitem{}
    \href{https://thinkingneuron.com/how-to-measure-the-correlation-between-two-categorical-variables-in-python/}{Thinking Neuron - How to Measure the Correlation Between Two Categorical Variables in Python}
    \bibitem{}
    \href{https://www.stratascratch.com/blog/chi-square-test-in-python-a-technical-guide/}{StrataScratch - Chi-Square Test in Python: A Technical Guide}
    \bibitem{}
    \href{https://en.wikipedia.org/wiki/Cram\%C3\%A9r\%27s\_V}{Wikipedia - Cramér's V}
    \bibitem{}
    \href{https://saturncloud.io/blog/how-to-detect-and-exclude-outliers-in-a-pandas-dataframe/}{Saturn Cloud - How to Detect and Exclude Outliers in a Pandas DataFrame}
    \bibitem{}
    \href{https://www.kaggle.com/discussions/questions-and-answers/159183}{Kaggle - When to standardize test and train data?}
    \bibitem{}
    \href{https://scikit-learn.org/stable/modules/preprocessing.html#standardization-or-mean-removal-and-variance-scaling}{Scikit-Learn - Standardization or Mean Removal and Variance Scaling}
    \bibitem{}
    \href{https://scikit-learn.org/stable/modules/generated/sklearn.preprocessing.OneHotEncoder.html}{Scikit-Learn - OneHotEncoder}
    \bibitem{}
    \href{https://scikit-learn.org/stable/modules/generated/sklearn.preprocessing.LabelEncoder.html}{Scikit-Learn - LabelEncoder}
    \bibitem{}
    \href{https://towardsdatascience.com/understanding-confusion-matrix-a9ad42dcfd62}{Towards Data Science - Understanding Confusion Matrix}
